Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report

### 2024-03-31 paper.R1.qmd
Code cleanup

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: 
  - name: Caroline B. Smith
    affiliation:
     - id: wsu
       department: Department of Anthropology
       name: Washington State University
  - name: Edward H. Hagen
    affiliation:
     - ref: wsu
date: today
format:
  docx:
    number-sections: true
  html:
    embed-resources: true
execute:
  echo: false
  warning: false
csl: apa.csl
bibliography: paper.bib
crossref:
  custom:
    - kind: float
      reference-prefix: Figure S
      key: sfig
      space-before-numbering: false
    - kind: float
      reference-prefix: Table S
      key: stbl
      space-before-numbering: false
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(psych)
library(xtable)
library(knitr)
library(kableExtra)
library(weights)
library(jtools)
library(reshape2)
library(ggcorrplot)
library(patchwork)
library(modelsummary)
source('analysis.v2.R')
```

@@

```{r}
#| label: fig-coefs
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95% CIs. For the full models, see the SI.

@@

We used simulations to estimate our power to detect strength effects that were 75% as large as the ones observed in our pilot study, and sex interaction effects that were equal in magnitude but opposite in sign to the strength effects (i.e., no effect of strength on mating success in women), with a sample size equal to that in our unobserved data. We are confident that we have sufficient power to detect true strength effects somewhat less than the ones observed in our pilot study (@tbl-power). We are less confident in our power to detect true sex interaction effects because, all else equal, power to detect interaction effects is generally lower than main effects, and in our simulations we used large interaction effects equal in magnitude to the main effects, which is probably unrealistic.

>>>>

---
title: "Grip strength, mating success, and immune and energy costs in a population sample of US women and men: a registered report"
author: 
  - name: Caroline B. Smith
    affiliation:
     - id: wsu
       department: Department of Anthropology
       name: Washington State University
  - name: Edward H. Hagen
    affiliation:
     - ref: wsu
date: today
format:
  html:
    toc: true
    embed-resources: true
  # docx:
  #   number-sections: true
execute:
  echo: false
  warning: false
csl: apa.csl
bibliography: paper.bib
crossref:
  custom:
    - kind: float
      reference-prefix: Figure S
      key: sfig
      space-before-numbering: false
    - kind: float
      reference-prefix: Table S
      key: stbl
      space-before-numbering: false
---

```{r}
library(ggcorrplot)
library(modelsummary)
source('analysis.R1.R')
```

@@

```{r}
#| label: fig-coefs
#| fig-width: 10
#| fig-height: 8
#| fig-cap: Coefficients of sex-specific strength, and strength X sex interaction for our four mating success outcomes and our five sets of potential confounding variables. Partnered coefficients are from logistic regressions, partner number coefficients are from quasi-Poisson glm regressions, and age at first sex coefficients are from Gaussian glm regressions. Bars are 95\% CIs. For the full models, see the SI.

@@

We used simulations to estimate our power to detect strength effects that were 75% as large as the ones observed in our pilot study, and sex interaction effects that were equal in magnitude but opposite in sign to the strength effects (i.e., no effect of strength on mating success in women), with a sample size equal to that in our unobserved data. We are confident that we have sufficient power to detect true strength effects somewhat less than the ones observed in our pilot study (@tbl-power). We are less confident in our power to detect true sex interaction effects because, all else equal, power to detect interaction effects is generally lower than main effects.
